Many Analystis Project

### 2022-03-12 analysis-religious-final.Rmd
delete figs

```{r runanalysis, echo=FALSE, include = FALSE}
# source("libs.R") # libraries 
# source("funs.R") # custom functions
library("tidyverse")
library("easystats")
library("ggplot2") #plots
#library("sjstats") #test statistics
#library("sjPlot")
#library("sjmisc")
##library("insight")
#library("see")
#library("performance")
library("ggraph")
#library("parameters")
library("lme4")
#library("psych") ## correlation matrix
library("table1")
library("ggeffects")
#library("gghighlight")
#library("texreg")
library("kableExtra")
#library("naniar") # missingness
library("Amelia")
#library("magrittr")
library("patchwork")
library("texreg")
library("viridisLite")
library("patchwork")
library("here")
#library("rethinking")
#library("statsExpressions")
#library("ggstatsplot")
library("ggthemes")
=library("rstan")
library("brms")
library("bayesplot")
library("bayesplot")
library("dagitty")
library("ggdag")
library("geepack")  # marginal structural models
library("ipw") # inverse probability weighting. 
library("WeightIt")# inverse probability weighting. 
library("emmeans")
library("splines")
rstan_options(auto_write=TRUE)
options(mc.cores=parallel::detectCores ())
theme_set(theme_few())
cite_packages(include_R = TRUE)

@@

>>>>

```{r runanalysis, echo=FALSE, include = FALSE}
# source("libs.R") # libraries 
# source("funs.R") # custom functions
library("tidyverse")
library("easystats")
library("ggraph")
library("lme4")
library("table1")
library("ggeffects")
library("kableExtra")
library("naniar") # missingness
library("Amelia")
library("patchwork")
library("texreg")
library("viridisLite")
library("patchwork")
library("here")
library("ggthemes")
=library("rstan")
library("brms")
library("bayesplot")
library("bayesplot")
library("dagitty")
library("ggdag")
library("geepack")  # marginal structural models
library("ipw") # inverse probability weighting. 
library("WeightIt")# inverse probability weighting. 
library("emmeans")
library("splines")
rstan_options(auto_write=TRUE)
options(mc.cores=parallel::detectCores ())
theme_set(theme_few())
cite_packages(include_R = TRUE)

@@

```{r}
sim_fun_A = function() {
  n <- 1000
  U <- rnorm(n, 1) # unmeasured distress 
  A <- rnorm(n, 1) # religious service attendance,
  M <- rnorm(n , A + .2 * U)# religious identification
  Y <- rnorm(n , - A *.2 + U *.4) #  distress reduced by attendance.

# simulate data
simdat_A <- data.frame(
  M = M, # rel identification
  A = A, # rel service
  U = U, # distressing events (unmeasured)
  Y = Y )# outcome

# mediator attenuates true effect ~ .1 instead of ~.1
parameters::pool_parameters(r_lm_A)

## Repeat but with no mediator in model
set.seed(123)
sim_fun_B = function() {
  n <- 1000
  U <- rnorm(n, 1) # unmeasured distress 
  A <- rnorm(n, 1) # religious service attendance,
  M <- rnorm(n , A + .2 * U)# religious identification
  Y <- rnorm(n , - A *.2 + .4 * U) #  distress reduced by attendance.

# Simulate data
simdat_B <- data.frame(
  M = M, # rel identification
  A = A, # rel service attendance
  U = U, # distressing events (unmeasured)
  Y = Y ) # outcome

# Only model exposure
sim_B <- lm(Y ~ A, data = simdat_B)
sim_B
}

# Replication 100xs
r_lm_B <- NA
r_lm_B = replicate(100, sim_fun_B(), simplify = FALSE )

# diminished recover true effect ~ .2
parameters::pool_parameters(r_lm_B)
